# Calculation: Nigeria 2021 post-cycle coverage

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(readxl)
library(knitr)
library(zoo)
library(scales)
library(gt)
options(knitr.kable.NA = '')
```

## Nigeria post-cycle coverage, total, weighted by target population (added by GiveWell)

The calculation from this sheet relies on target populations from Table 8 from [Malaria Consortium, 2021 SMC coverage report, Burkina Faso, Chad, Mozambique, Nigeria, Togo, and Uganda](https://files.givewell.org/files/DWDA%202009/Malaria%20Consortium/Malaria_Consortium_2021_SMC_coverage_report_Burkina_Faso_Chad_Mozambique_Nigeria_Togo_and_Uganda.pdf).  We only need the target populations for children 5 and under, so we choose that subset of the table.

This is using the target population from Nasarawa[2] row.

>The target population for Nasarawa was overestimated in 2021. The target population for Nasarawa was revised downwards after cycle 2 and administrative coverage re-estimated.
>
> --Malaria Consortium, 2021 SMC coverage report, Burkina Faso, Chad, Mozambique, Nigeria, Togo, and Uganda. Pg. 31

If we changed this to the 952,480 target population, which was the original estimate, then the total target population for Nigeria would match that reported in Table 1, Pg. 11 (8,399,151): 
8,041,804 + (952,480 - 595,133) = 8,399,151

We are using the updated figure, because it is more accurate.  Below, we change the name of Nasarawa2 -> Nasarawa.  In the join operation later, the old numbers corresponding to Nasawawa1 will be dropped.

```{r}
t_8 = read_excel("sources/2021/malaria-consortium-2021-table-08.xlsx", 
                 sheet = "Sheet1", col_names = FALSE, 
                 skip = 3, n_max = 28) |>
  select(1:4) |>
  rename(country = 1, state = 2, age_group = 3, target_pop = 4) |>
  mutate(country = na.locf(country),
         state = na.locf(state)) |>
  filter(age_group == '3–59 months') |>
  select(-age_group) |>
  mutate(state = case_when(state == 'Nasarawa2' ~ 'Nasarawa',
                           TRUE ~ state)) |>
  suppressMessages()
```

We then join the target population numbers to our data from tables 15 and 16.  Then we calculate summary statistics, both for the 4-cycle and 5-cycle groups, then grand totals.

```{r}
load("data/2021/post-cycle-coverage.R")
t_1516 |>
  left_join(t_8, join_by(country, state)) |>
  select(state, target_pop, p_hat, n_cycles, survey) |>
  pivot_wider(id_cols = c(state, target_pop, n_cycles),
              names_from = survey,
              values_from = p_hat) |>
  group_by(n_cycles) |>
  gt() |>
  fmt_percent(
    columns = 3:8,
    decimals = 1
  ) |>
  fmt_number(columns = 2, decimals = 0) |>
  sub_missing() |>
  summary_rows(
    columns = target_pop,
    fns = list('Group Total' = ~ sum(.)),
    fmt = ~fmt_number(., decimals = 0)
  ) |>
  summary_rows(
    columns = 3:8,
    fns = list('Group Total' = ~ weighted.mean(x=., w=target_pop, na.rm = TRUE)),
    fmt = ~fmt_percent(., decimals = 1)
  ) |>
  grand_summary_rows(
    columns = target_pop,
    fns = list('Total' = ~ sum(.)),
    fmt = ~fmt_number(., decimals = 0)
  ) |>
  grand_summary_rows(
    columns = 3:8,
    fns = list('Total' = ~ weighted.mean(x=., w=target_pop, na.rm = TRUE)),
    fmt = ~fmt_percent(., decimals = 1)
  )
```


## Error in Original Calculations {#sec-calculation-error}

There is one discrepancy between this table and [GiveWell's spreadsheet](https://docs.google.com/spreadsheets/d/1WqNL0PEA4cT470ALp0nItEEU8gM_IlhVNIJK1GqnFVE/edit?gid=1419867728#gid=1419867728) cells `F7`, `F8`, and `F14`.  This is because the original spreadsheet has the incorrect forumla in `F7`. The formula it ought to have in `F7` is `=C34`.  The correct value in cell `F7` is `90.4%`.  This incorrect value then affects the totals in `F8` and `F14`.

## Tables 15 and 16

The tables below are from [Malaria Consortium, 2021 SMC coverage report, Burkina Faso, Chad, Mozambique, Nigeria, Togo, and Uganda](https://files.givewell.org/files/DWDA%202009/Malaria%20Consortium/Malaria_Consortium_2021_SMC_coverage_report_Burkina_Faso_Chad_Mozambique_Nigeria_Togo_and_Uganda.pdf)

These tables are also introduced in @sec-post-cycle.

### Table 15: Proportions of eligible who received day 1 SPAQ, by Nigerian state and survey (states with four cycles)

```{r}
read_excel("sources/2021/malaria-consortium-2021-table-15.xlsx") |>
  kable(caption = "Table 15")
```

### Table 16: Proportions of eligible who received day 1 SPAQ, by Nigerian state and survey (states with five cycles)

```{r}
read_excel("sources/2021/malaria-consortium-2021-table-16.xlsx") |>
  kable(caption = "Table 16")
```



