# Source: 2021 SMC cycles received per child {#sec-smc-per-child}

The table below is from [Malaria Consortium, 2021 SMC coverage report, Burkina Faso, Chad, Mozambique, Nigeria, Togo, and Uganda](https://files.givewell.org/files/DWDA%202009/Malaria%20Consortium/Malaria_Consortium_2021_SMC_coverage_report_Burkina_Faso_Chad_Mozambique_Nigeria_Togo_and_Uganda.pdf)

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(readxl)
library(knitr)
library(zoo)
options(knitr.kable.NA = '')
```

## Table 25: Proportions of eligible children (3–59 months) who received day 1 SPAQ by community distributors by number of cycles during 2021 (EoR survey), by country

Because of the merged cells and combined variables, we tidy this table up before displaying it.

```{r}
t_25 <-read_excel("sources/2021/malaria-consortium-2021-table-25.xlsx",
           col_types = c("text", "numeric", "numeric", "text")) |>
  rename(cycle = 1, n = 2, p_hat = 3, c_interval = 4) |>
  mutate(country = case_when(is.na(p_hat) ~ cycle,
                              TRUE ~ NA),
         country = na.locf(country),
         n = c(NA, na.locf(n))) |>
  filter(!is.na(p_hat)) |>
  separate_wider_delim(cols = country,
                       delim = "(",
                       names = c("country", "country_note"),
                       too_few = "align_start") |>
  mutate(country_note = str_sub(country_note, end = -2)) |>
  separate_wider_delim(cols = c_interval,
                       delim = '-',
                       names = c("left_ci", "right_ci")) |>
  mutate(left_ci = as.numeric(left_ci)/100,
         right_ci = as.numeric(right_ci)/100)

t_25 |>
  kable(caption = "Table 25")
```
