# Source: Targetted Populations

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(readxl)
library(knitr)
library(zoo)
library(scales)
library(gt)
options(knitr.kable.NA = '')
```

## Targetted Population by Country

```{r}
t_1 <- read_excel("sources/2021/malaria-consortium-2021-table-01.xlsx", 
                 sheet = "Sheet1", n_max = 8) |>
  separate_wider_delim(cols = 1,
                       delim = "(",
                       too_many = "drop",
                       names = "country") |>
  separate_wider_delim(cols = 3,
                       delim = "(",
                       too_many = "drop",
                       names = "target_pop") |>
  select(country, target_pop) |>
  mutate(target_pop = as.numeric(gsub(",","",target_pop)))

t_1 |> gt()
```


## Nigeria

This is using the target population from Nasarawa[2] row.

>The target population for Nasarawa was overestimated in 2021. The target population for Nasarawa was revised downwards after cycle 2 and administrative coverage re-estimated.
>
> --Malaria Consortium, 2021 SMC coverage report, Burkina Faso, Chad, Mozambique, Nigeria, Togo, and Uganda. Pg. 31

If we changed this to the 952,480 target population, which was the original estimate, then the total target population for Nigeria would match that reported in Table 1, Pg. 11 (8,399,151): 
$$8,041,804 + (952,480 - 595,133) = 8,399,151$$

We are using the updated figure, because it is more accurate.

```{r}
t_8 = read_excel("sources/2021/malaria-consortium-2021-table-08.xlsx", 
                 sheet = "Sheet1", col_names = FALSE, 
                 skip = 3, n_max = 28) |>
  select(1:4) |>
  rename(country = 1, state = 2, age_group = 3, target_pop = 4) |>
  mutate(country = na.locf(country),
         state = na.locf(state)) |>
  filter(age_group == '3–59 months') |>
  select(-age_group) |>
  mutate(state = case_when(state == 'Nasarawa2' ~ 'Nasarawa',
                           TRUE ~ state)) |>
  suppressMessages()

t_8 |> gt()
```

## Save the data

```{r}
save(list = c('t_1', 't_8'), file="data/2021/target_populations.R")
```


